---
title: "Support Vector Machine"
author: "Michael In der Au"
date: "6 Juni 2018"
output: 
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: true
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 2
    number_sections: true
---

# Vorbereitung
## Benötigte Pakete
```{r, warnings = FALSE, warning=FALSE, error=FALSE}
#required packages
library(e1071)
library(mice)
library(caret)
library(ggplot2)
library(dplyr)
library(Hmisc)
```

# Einlesen der Ausgangsdaten
```{r}
#read train data
train <- read.csv("data/cs-training.csv", header = T, sep = ",", dec = ".")
#exclude ids
train <- train[-c(1)]
#read test data
test <- read.csv("data/cs-test.csv", header = T, sep = ",", dec = ".")
#exclude ids
test <- test[-c(1)]

#view data
summary(train)
summary(test)
```

# Preprocessing

## Imputation der NAs 
```{r, eval = FALSE, warning=FALSE, error=FALSE}
# #imputation using MICE package
# imp <- mice(train, m=5, maxit=2, method='pmm', seed = 123)
# train_imputed <- complete(x = imp,action =  1)
# #summary(train_imputed)
# imp <- mice(test, m=5, maxit=2, method='pmm', seed = 123)
# test_imputed <- complete(x = imp,action =  1)
# 
# #export imputed data as .csv for future usage
# write.csv(test_imputed,"data/test_imputed.csv")
# write.csv(train_imputed,"data/train_imputed.csv")
```

## Kontrolle der imputierten Daten
```{r}
#read imputed data
train <- read.csv("data/train_imputed.csv")
test <- read.csv("data/test_imputed.csv")

#imputed data
summary(train)
summary(test)
```

## Datenbereinigung

### RevolvingUtilizationOfUnsecuredLines
```{r, warning=FALSE, error=FALSE}
#-RevolvingUtilizationOfUnsecuredLines
#-- (total balance) / (total credit limit)

# the closer this value is to 100% the more the consumer is using the credit limit 
summary(train$RevolvingUtilizationOfUnsecuredLines)
mis <-train %>%
  filter(train$RevolvingUtilizationOfUnsecuredLines > 1)
summary(mis)

#percentage of regressor > 1 in train data
nrow(mis)/nrow(train)*100

#apply coded value -1 to outliers
train$RevolvingUtilizationOfUnsecuredLines[train$RevolvingUtilizationOfUnsecuredLines > 1] <- -1

summary(train$RevolvingUtilizationOfUnsecuredLines)
```

### Age
```{r}
#-age

summary(train$age)
mis <- train %>%
  filter(train$age == 0)
nrow(mis)

#omit line with age = 0
train <- subset(train, age > 0)

summary(train$age)  
```

### NumberOfTime30_59DaysPastDueNotWorse
```{r}
#-NumberOfTime30_59DaysPastDueNotWorse

summary(train$NumberOfTime30_59DaysPastDueNotWorse)
summary(train$NumberOfTime60_89DaysPastDueNotWorse)
summary(train$NumberOfTimes90DaysLate)

#it can be assumed that 96 and 98 are coded values of some kind, 
#because both values have their own meaning they cant be ommited
# and have to be encoded
nrow(subset(train, train$NumberOfTime30_59DaysPastDueNotWorse >=15))
n_96 <- nrow(subset(train, train$NumberOfTime30_59DaysPastDueNotWorse ==96))
n_98 <- nrow(subset(train, train$NumberOfTime30_59DaysPastDueNotWorse ==98))

(n_96+n_98)/nrow(train)*100

train$NumberOfTime30_59DaysPastDueNotWorse[train$NumberOfTime30_59DaysPastDueNotWorse >= 15]<- -1

summary(train$NumberOfTime30_59DaysPastDueNotWorse)
```

### NumberOfTime60_89DaysPastDueNotWorse, NumberOfTimes90DaysLate
```{r}
#the same approach applies to NumberOfTime60_89DaysPastDueNotWorse and
#NumberOfTimes90DaysLate
nrow(subset(train, train$NumberOfTime60_89DaysPastDueNotWorse >=15))
n_96 <- nrow(subset(train, train$NumberOfTime60_89DaysPastDueNotWorse ==96))
n_98 <- nrow(subset(train, train$NumberOfTime60_89DaysPastDueNotWorse ==98))

(n_96+n_98)/nrow(train)*100

train$NumberOfTime60_89DaysPastDueNotWorse[train$NumberOfTime60_89DaysPastDueNotWorse >= 15] <- -1

summary(train$NumberOfTime60_89DaysPastDueNotWorse)

summary(train$NumberOfTimes90DaysLate)
nrow(subset(train, train$NumberOfTimes90DaysLate >=19))
n_96 <- nrow(subset(train, train$NumberOfTimes90DaysLate ==96))
n_98 <- nrow(subset(train, train$NumberOfTimes90DaysLate ==98))

(n_96+n_98)/nrow(train)*100

train$NumberOfTimes90DaysLate[train$NumberOfTimes90DaysLate >= 19] <- -1

summary(train$NumberOfTimes90DaysLate)
```

### Debt ratio
```{r}
#- DebtRatio
#-- (total debts) / (monthly income)
#-- thus, values > 1 indicate more debts than income

summary(train$DebtRatio)
summary(train$MonthlyIncome)

#monthly income is the denominator of debt ratio thus it cannot be 0
#percentage of regressor > 1 in train data
n_inc0 <- nrow(subset(train, train$MonthlyIncome ==0))
n_inc0/nrow(train)*100

#if the monthly salary is equal to zero it is replaced by -1 

index <- train$MonthlyIncome == 0
train$DebtRatio[index] <- -1
summary(train$MonthlyIncome)

#if the monthly income is missing, it is replaced by 1

train$MonthlyIncome[is.na(train$MonthlyIncome)] <- 1

summary(train$DebtRatio)
```

### Monthly income
```{r}
#-Monthly income

summary(train$MonthlyIncome)

n_inc50k <- nrow(subset(train, train$MonthlyIncome >50000))
n_inc50k/nrow(train)*100

#omit outliers
train <- subset(train, MonthlyIncome < 50000)
```

### NumberOfOpenCreditLinesAndLoans
```{r}
#-NumberOfOpenCreditLinesAndLoans

summary(train$NumberOfOpenCreditLinesAndLoans)

#omit outliers in the 99th percentile

nrow(train[train$NumberOfOpenCreditLinesAndLoans < quantile(train$NumberOfOpenCreditLinesAndLoans, 0.99),])
train <- train[train$NumberOfOpenCreditLinesAndLoans < quantile(train$NumberOfOpenCreditLinesAndLoans, 0.99),]
summary(train$NumberOfOpenCreditLinesAndLoans)
```

### NumberOfDependents
```{r}
#-NumberOfDependents

summary(train$NumberOfDependents)

#omit outliers in the 99th percentile

nrow(train[train$NumberOfDependents < quantile(train$NumberOfDependents, 0.99),])
train <- train[train$NumberOfDependents < quantile(train$NumberOfDependents, 0.99),]
summary(train$NumberOfDependents)
```

## Abschluss
```{r}
summary(train)

#remove ids
train <- train[-1]
test <- test[-1]
```

# Modellierung

## Paket e1071
```{r, eval=FALSE}
#seed for reproducibility
set.seed(123)

#svm classifier using e1071
library(e1071)

classifier_rbf <- svm(formula = SeriousDlqin2yrs ~ ., 
                  data = train, 
                  type = "C-classification", 
                  kernel = "radial")
```

## Paket kernlab
```{r, warning=FALSE, error=FALSE}
#using kernlab 
library(kernlab)

mod <- ksvm(train$SeriousDlqin2yrs~.,
            data = train,
            kernel = "rbfdot",
            prob.model = TRUE)
#model overview
mod
#number of support vectors
mod@nSV
#line number of support vectors in the trainset
mod@alphaindex
#alpha values
mod@alpha
#hyperplane coefficiants
# mod@coef
#negative intercept
mod@b
#error on of the seperating hyperplane on the trainset
mod@error
#prediction
u <- predict(mod, train)
#confusion matrix
# table(u,t(tmp[1]))
#z scores
# mod@xmatrix
#scaled values
mod@scaling$scaled
#coefficiants
mod@coef[[1]][1]
mod@coef[[1]][2]
#prediction on the test set
pred.test <- predict(mod, test, type = "response")
summary(pred.test<0)

```